Medical Concept Extraction

### 2012-12-17 paper/paper.tex
Updating results table.
Updating prev_ feature section.

\usepackage{paralist}
\usepackage{graphicx}
\usepackage{url}
\usepackage{amsmath}
\usepackage{setspace}

@@

\subsubsection{Previous}
We take a basic approach to context features by considering the immediately preceding word for each individual word. Given a word with the feature set previously described, we simply duplicate each feature with the corresponding value for it's previous neighbor and rename these features $previous\_$<NAME> (for example, $previous\_$length).  This serves to double the size of our feature space.
\subsubsection{Next}
Likewise, we duplicate the subsequent word features, which are relabeled as $next\_$<NAME>. At this point, our feature space is tripled, but was already quite large--hence, we decided only to consider surrounding words at a bigram level. Nevertheless, this relatively straightforward step brought out CRF F1 testing score up to 0.98.

@@

\begin{figure}
\begin{center}

	\begin{tabular}{|l|l|l|}
	\hline
	{\bf Feature Set} & {\bf Classifier} & {\bf F1 Score}  \\ \hline
	All except ``line'' &  crfsuite &  0.0765  \\ \hline

	\end{tabular}

\end{center}
\caption{A summary of the F1-scores from many different models with different features enabled.}
\label{fig:summary_f1_scores}
\end{figure}

>>>>

\usepackage{paralist}
\usepackage{graphicx}
\usepackage{url}
\usepackage{amsmath}
\usepackage{setspace}
\usepackage{rotating}

@@

\subsubsection{Previous}
We take a basic approach to context features by considering the immediately preceding word for each individual word. Given a word with the feature set previously described, we simply duplicate each feature with the corresponding value for it's previous neighbor and rename these features $prev\_$<NAME> (e.g. $prev\_$length).  This serves to double the size of our feature space.
\subsubsection{Next}
Likewise, we duplicate the subsequent word features, which are relabeled as $next\_$<NAME>. At this point, our feature space is tripled, but was already quite large--hence, we decided only to consider surrounding words at a bigram level. Nevertheless, this relatively straightforward step brought out CRF F1 testing score up to 0.98.

@@

\begin{figure*}

\begin{center}
	\begin{tabular}{|l|l|l|l|l|l|l|l|l|l|l||l|l|}
	\hline
	\multicolumn{11}{|c||}{\bf Feature Set} & \multicolumn{2}{|c|}{\bf F1 Score}	\\ \hline
		\begin{sideways} length \end{sideways} & 
		\begin{sideways} mitre \end{sideways} & 
		\begin{sideways} next \end{sideways} & 
		\begin{sideways} pos \end{sideways} & 
		\begin{sideways} prev \end{sideways} & 
		\begin{sideways} stem\_lancaster \end{sideways} & 
		\begin{sideways} stem\_porter \end{sideways} & 
		\begin{sideways} stem\_wordnet \end{sideways} & 
		\begin{sideways} test\_result \end{sideways} & 
		\begin{sideways} word \end{sideways} & 
		\begin{sideways} word\_shape \end{sideways} & 
	LIN & CRF	\\ \hline

	\checkmark & & & & & & & & & & & &	\\ \hline
	& \checkmark & & & & & & & & & & &	\\ \hline
	& & \checkmark & & & & & & & & & &	\\ \hline
	& & & \checkmark & & & & & & & & &	\\ \hline
	& & & & \checkmark & & & & & & & &	\\ \hline
	& & & & & \checkmark & & & & & & &	\\ \hline
	& & & & & & \checkmark & & & & & &	\\ \hline
	& & & & & & & \checkmark & & & & &	\\ \hline
	& & & & & & & & \checkmark & & & &	\\ \hline
	& & & & & & & & & \checkmark & & &	\\ \hline
	& & & & & & & & & & \checkmark & &	\\ \hline

\end{tabular}
\end{center}
\caption{A summary of the F1-scores from many different models with different features enabled.}
\label{fig:summary_f1_scores}
\end{figure*}
